The Two Dualities of Computation: Negative and Fractional Types

### 2012-03-11 rational.tex
sec negative types

%\subsection{Compact Closure with Additive Inverses}
\emph{Coherence for Compact Closure with Additive Duality.}  The
appropriate coherence condition for Compact Closed Categories,
expressed as the triangle axiom, is satisfied by {{eta+}}/{{eps+}} and
may be visualized (modulo {{0}} wires, swapping etc.) as explained by
Selinger \cite{springerlink:10.1007/978-3-642-12821-94} as the
operational equivalence:

>>>>

%\subsection{Compact Closure with Additive Inverses}
\emph{Coherence for Compact Closure with Additive Duality.}  The
appropriate coherence condition for compact closed categories,
expressed as the triangle axiom, is satisfied by {{eta+}}/{{eps+}} and
may be visualized (modulo {{0}} wires, swapping etc.) as explained by
Selinger \cite{springerlink:10.1007/978-3-642-12821-94} as the
operational equivalence:
